Type Refinements for the Working Class

### 2015-11-11 paper.tex
corrections

Next, we define hypothetico-general (or \emph{functional}) refinement
$\HEqRefines{\Phi}{\Psi}{\phi}{\psi}{\tau}$ in terms of parametric refinement,
simultaneously with parametric context refinement
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ and functional equality
$\HRMemEq{\Phi}{\Psi}{M}{N}{\phi}$. We will write
$\HRefines{\Phi}{\Psi}{\phi}{\tau}$ as a shorthand for
$\HEqRefines{\Phi}{\Psi}{\phi}{\phi}{\tau}$.

@@

Functional refinement $\HRefines{\Phi}{\Psi}{\phi}{\tau}$ presupposes
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ and $\IsSort{\tau}$, and is explained by
induction on the evidence for its first presupposition.

\paragraph{Case} $\DefPRefinesCtxNil{\Phi}$.
\[
  \infer{
    \HRefines{\Phi}{\cdot}{\phi}{\tau}
  }{
    \Refines{\Phi}{\phi}{\tau}
  }
\]

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\psi}{\Gamma}{\sigma}$.
\begin{gather*}
  \infer{
    \HRefines{\Phi}{\Psi,x:\psi}{\phi}{\tau}
  }{
    \GenJ{y,z:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{\Subst{y}{x}{\phi}}{\Subst{z}{x}{\phi}}{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{y}{z}{\phi}
      }
    }
  }
\end{gather*}

>>>>

Next, we define functional refinement
$\HEqRefines{\Phi}{\Psi}{\phi}{\psi}{\tau}$ in terms of parametric refinement,
simultaneously with parametric context refinement
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ and functional equality
$\HRMemEq{\Phi}{\Psi}{M}{N}{\phi}$. We will write
$\HRefines{\Phi}{\Psi}{\phi}{\tau}$ as a shorthand for
$\HEqRefines{\Phi}{\Psi}{\phi}{\phi}{\tau}$.

\todo[inline]{%
  Properly express the \emph{syntactic} presuppositions of the sequent
  judgments so that the use of hypothetical and general judgment is
  well-formed.
}

@@

Functional refinement $\HEqRefines{\Phi}{\Psi}{\phi}{\psi}{\tau}$ presupposes
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ and $\IsSort{\tau}$, and is explained by
induction on the evidence for its first presupposition.

\paragraph{Case} $\DefPRefinesCtxNil{\Phi}$.
\[
  \infer{
    \HEqRefines{\Phi}{\cdot}{\phi}{\psi}{\tau}
  }{
    \EqRefines{\Phi}{\phi}{\psi}{\tau}
  }
\]

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\chi}{\Gamma}{\sigma}$.
\begin{gather*}
  \infer{
    \HEqRefines{\Phi}{\Psi,x:\chi}{\phi}{\psi}{\tau}
  }{
    \GenJ{y,z:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{\Subst{y}{x}{\phi}}{\Subst{z}{x}{\psi}}{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{y}{z}{\chi}
      }
    }
  }
\end{gather*}
